---
title: "TBI Prevalence Figures"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
# rm(list = ls(all.names = TRUE))
# gc()
library(tidyverse)
library(gt)
library(readxl)
library(spatstat)
```

## Read in Files

```{r}
tbi_2001 <- readRDS("estimates_2001_iso3_v1.rds")
View(tbi_2001)

tbi_2006 <- readRDS("estimates_2006_iso3_v1.rds")


tbi_2011 <- readRDS("2011estimates_iso3_v1.rds")


tbi_2016 <- readRDS("2016 estimates_iso3.rds")
View(tbi_2016$LTBP)

tb_inc <- readRDS("incidence.rds")
colnames(tb_inc) <- c("ISO3", "WHO_Region", "e_inc_100k")
tb_inc <- tb_inc%>%select(-WHO_Region)

countries_168 <- read_xlsx("/Users/ajordan/Library/CloudStorage/OneDrive-McGillUniversity/LTBI-Aust-CEA-master/Data/countries 168.xlsx")

#View(countries_168)
```



## Apply Function to Files


```{r}
grouping_function <- function(df){
  
  tbi_data <- merge(df, tb_inc, by = "ISO3")
# Less bands
  tbi_data_bands <- tbi_data%>%
    mutate(inc_band_per100k = ifelse(
      e_inc_100k < 10, "0-9 per 100,000 persons", ifelse(
        e_inc_100k >= 10 & e_inc_100k < 50, "10-49 per 100,000 persons", ifelse(
          e_inc_100k >= 50 & e_inc_100k < 100, "50-99 per 100,000 persons", ifelse(
            e_inc_100k >= 100 & e_inc_100k < 200, "100-199 per 100,000 persons",ifelse(
              e_inc_100k >= 200 & e_inc_100k <= 1000, "200+ per 100,000 persons", "No value"))))))
  
  tbi_data_bands$inc_band_per100k <- factor(tbi_data_bands$inc_band_per100k,
                                            levels = c("0-9 per 100,000 persons",
                                              "10-49 per 100,000 persons",
                                                       "50-99 per 100,000 persons",
                                                       "100-199 per 100,000 persons",
                                                       "200+ per 100,000 persons"))
  
  tbi_age_groups <- tbi_data_bands%>%
    mutate(AGE_BANDS = ifelse(
      AGEP < 15, "0-14", ifelse(
        AGEP >= 15 & AGEP < 35, "15-34", ifelse(
          AGEP >= 35 & AGEP < 55, "35-54",ifelse(
            AGEP >= 55 & AGEP < 75, "55-74",ifelse(
              AGEP >= 75 & AGEP <= 200, "75+", "No value"))))),
      AARP = YARP-YOBP)
  
  
  
 tbi_graph_aarp <- tbi_age_groups%>%
  mutate(AARP_BANDS = ifelse(
    AARP < 15, "AARP 0-14", ifelse(
      AARP >= 15 & AARP < 35, "AARP 15-34", ifelse(
        AARP >= 35 & AARP < 55, "AARP 35-54",ifelse(
          AARP >= 55 & AARP <= 74, "AARP 55-74", ifelse(
            AARP >= 75 & AARP <= 200, "AARP 75+", "No value"))))))%>%
   mutate(BPLP = recode(BPLP, `China, People's Republic of`="China"))%>%
   mutate(BPLP = ifelse(str_detect(BPLP, "Hong Kong"), "Hong Kong", 
                        ifelse(str_detect(BPLP, "United States"), "United States of America", BPLP)))
 
 # Restrict to 168 countries
 
  # tbi_168_countries <-  tbi_graph_aarp%>%
  #  filter(ISO3%in%c(countries_168$ISO3))
  # 
  # tbi_168_countries
}

tbi_2001_grouped <- grouping_function(tbi_2001)

tbi_2006_grouped <- grouping_function(tbi_2006)

tbi_2011_grouped <- grouping_function(tbi_2011)

tbi_2016_grouped <- na.omit(grouping_function(tbi_2016))

#View(tbi_2016_grouped)
tbi_all_census_years <- rbind(tbi_2001_grouped, tbi_2006_grouped, tbi_2011_grouped, tbi_2016_grouped)
View(tbi_all_census_years)


```


# Population Data
## Population tables made by pulling data directly from census unless certain calculations need to be made

Median and IQR-Age at Immigration and Age During Census Year
```{r}
summary_aarp <- tbi_all_census_years%>%
  group_by(CNSY)%>%
  summarize(median_aarp = weighted.median(AARP, NUMP),
            aarp_25 = weighted.quantile(AARP, NUMP, probs = 0.25),
            aarp_75 = weighted.quantile(AARP, NUMP, probs = 0.75))

summary_agep <-tbi_all_census_years%>%
  group_by(CNSY)%>%
  summarize(median_agep = weighted.median(AGEP, NUMP),
            agep_25 = weighted.quantile(AGEP, NUMP, probs = 0.25),
            agep_75 = weighted.quantile(AGEP, NUMP, probs = 0.75))

```
TBI Prevalence Overall
```{r}
overall_prevalence <- tbi_all_census_years%>%
  group_by(CNSY)%>%
  summarize(tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_ui_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_ui_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0))
```

Number Living in Canada by Age at Immigration
```{r top10, figures-side, fig.show="hold", out.width="50%", echo=FALSE}

aarp_NUMP_func <- function(df, CNSY){
  top10_total <- na.omit(df)%>%
    group_by(CNSY, AARP_BANDS)%>%
    summarise(NUMP=round(sum(NUMP), 0))%>%
    arrange(desc(NUMP))%>%
    slice_head(n=10)
  
  names(top10_total)[names(top10_total) == 'AARP_BANDS'] <- str_c("AARP_BANDS", CNSY)
  names(top10_total)[names(top10_total) == 'NUMP'] <- str_c("NUMP", CNSY)
  top10_total
}

pop_aarp_by_census <- cbind(aarp_NUMP_func(tbi_2001_grouped, " in 2001"),

aarp_NUMP_func(tbi_2006_grouped, " in 2006"),

aarp_NUMP_func(tbi_2011_grouped, " in 2011"),

aarp_NUMP_func(tbi_2016_grouped, " in 2016"))

pop_aarp_by_census

```

# Prevalence by Top 10 Common Countries of Origin 
```{r top10, figures-side, fig.show="hold", out.width="50%", echo=FALSE}

tbi_yarp_top10_func <- function(df, CNSY){
  top10_total1 <- na.omit(df)%>%
    group_by(BPLP)%>%
  summarise(NUMP=sum(NUMP),
    tbi_prev = round(median(Reduce("+",LTBP))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",LTBP), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",LTBP), 0.975)/sum(NUMP)*100,0))%>%
    arrange(desc(NUMP))%>%
    slice_head(n=10)
  

  
  top10_total <- top10_total1%>%select(BPLP, 
                            tbi_prev,
                            tbi_prev_95_low,
                            tbi_prev_95_high)
  
   names(top10_total)[names(top10_total) == 'BPLP'] <- str_c("BPLP", CNSY)
  top10_total

}
tbi_prev_coo_by_census <- cbind(tbi_yarp_top10_func(tbi_2001_grouped, " in 2001"),

tbi_yarp_top10_func(tbi_2006_grouped, " in 2006"),

tbi_yarp_top10_func(tbi_2011_grouped, " in 2011"),

tbi_yarp_top10_func(tbi_2016_grouped, " in 2016"))

tbi_prev_coo_by_census

```



# TB Disease Incidence in Country of Origin-Number Living in Canada, Proportion, and TBI Prevalence
```{r inc, figures-side, fig.show="hold", out.width="50%", echo=FALSE}

add_pop <- tbi_all_census_years%>%
    group_by(CNSY)%>%
  mutate(tot_pop = sum(NUMP))

#View(add_pop)

tbi_inc_tabprep <- unique(add_pop %>%
                              filter(NUMP > 0)%>%
    group_by(CNSY, inc_band_per100k)%>%
    summarise(pop_tot_group = sum(NUMP),
      proportion_pop=round((sum(NUMP)/tot_pop)*100, 2),
                  tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))


View(tbi_inc_tabprep)

tbi_inc_tab <- pivot_wider(tbi_inc_tabprep, names_from = "CNSY", values_from = c("proportion_pop", "tbi_prev"))
View( tbi_inc_tab)

```


# Age at Immigration-Number and Proportion Living in Canada, and Prevalence per Census Year
```{r aarp, figures-side, fig.show="hold", out.width="50%", echo=FALSE, include=FALSE}

tbi_age_tabprep <- unique(add_pop %>%
                              filter(NUMP > 0)%>%
    group_by(CNSY, AARP_BANDS)%>%
    summarise(pop_tot_group = sum(NUMP),
              proportion_pop=round((sum(NUMP)/tot_pop)*100, 2),
                  tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))

              

View(tbi_age_tabprep)
  
tbi_age_at_imm_tabprep <- pivot_wider(tbi_age_tabprep, names_from = "CNSY", values_from = c("proportion_pop", "tbi_prev"))
View( tbi_age_at_imm_tabprep )
# View( tbi_age_at_imm_tabprep%>%select(AARP_BANDS, 
#                                       proportion_pop_2001,
#                                       proportion_pop_2006,
#                                       proportion_pop_2011,
#                                       proportion_pop_2016))

```

Age during Census Year-Proportion Living in Canada and Prevalence per Census Year (Number living in Canada is in census data)
```{r agep}
 tbi_age_tabprep <- unique(add_pop %>%
                              filter(NUMP > 0)%>%
    group_by(CNSY, AGE_BANDS)%>%
    summarise(proportion_pop=round((sum(NUMP)/tot_pop)*100, 2),
                  tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0))

View(tbi_age_tabprep)
  
```


Prevalence among those who Immigrated in last 2 years-Total and by TB Disease Incidence in Country of Origin
```{r}
# Total
tbi_2years_imm <- unique(add_pop %>%
                                 filter(NUMP > 0 & !is.na(NUMP))%>%
                                filter(YARP > 2014)%>%
                                filter(CNSY==2016)
    summarise(
    tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))
    
View(tbi_2years_imm)
  

# By incidence in COO
tbi_2years_imm_inc_band <- unique(add_pop %>%
                                 filter(NUMP > 0 & !is.na(NUMP))%>%
                                filter(YARP > 2014)%>%
                                filter(CNSY==2016)%>%
    group_by(inc_band_per100k)%>%
    summarise(
    tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))
    
View(tbi_2years_imm_inc_band)
```

YARP Increments and Age During Census Year
```{r agep-inc}
tbi_yarp_agep_tabprep <- unique(add_pop%>%
                              filter(NUMP > 0 & CNSY=="2016")%>%
                                mutate(YARP_BANDS=ifelse(
      YARP >= 2012, "0-4 years since immigration", ifelse(
        YARP >= 2007 & YARP < 2012, "5-9 years since immigration", ifelse(
          YARP >= 2002 & YARP < 2007, "10-14 years since immigration",ifelse(
            YARP >= 1997 & YARP < 2002, "15-19 years since immigration",ifelse(
              YARP >= 1000 & YARP < 1997, "20+ years since immigration", "No value"))))))%>%
    group_by(YARP_BANDS, AGE_BANDS)%>%
    summarise(tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))

tbi_yarp_agep_tabprep$YARP_BANDS <- factor(tbi_yarp_agep_tabprep$YARP_BANDS, 
                                          levels = c("0-4 years since immigration",
                                                     "5-9 years since immigration",
                                                     "10-14 years since immigration",
                                                     "15-19 years since immigration",
                                                     "20+ years since immigration"))

#View(tbi_yarp_agep_tabprep)

tbi_yarp_agep_med <- tbi_yarp_agep_tabprep%>%
  select(YARP_BANDS, AGE_BANDS, tbi_prev)%>%
  pivot_wider(names_from = AGE_BANDS,
              values_from = tbi_prev)

tbi_yarp_agep_low <-tbi_yarp_agep_tabprep%>%
  select(YARP_BANDS, AGE_BANDS, tbi_prev_95_low)%>%
  pivot_wider(names_from = AGE_BANDS,
              values_from = tbi_prev_95_low)

tbi_yarp_agep_high <- tbi_yarp_agep_tabprep%>%
  select(YARP_BANDS, AGE_BANDS, tbi_prev_95_high)%>%
  pivot_wider(names_from = AGE_BANDS,
              values_from = tbi_prev_95_high)

# Total-YARP by Census Year

tbi_yarp_inc_tabprep_total <- unique(add_pop %>%
                              filter(NUMP > 0 & CNSY=="2016")%>%
                                mutate(YARP_BANDS=ifelse(
      YARP >= 2012, "0-4 years since immigration", ifelse(
        YARP >= 2007 & YARP < 2012, "5-9 years since immigration", ifelse(
          YARP >= 2002 & YARP < 2007, "10-14 years since immigration",ifelse(
            YARP >= 1997 & YARP < 2002, "15-19 years since immigration",ifelse(
              YARP >= 1000 & YARP < 1997, "20+ years since immigration", "No value"))))))%>%
    group_by(CNSY, YARP_BANDS)%>%
    summarise(tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))

View(tbi_yarp_inc_tabprep_total)

# AGEP v YARP
# tbi_yarp_agep_tabprep_total <- unique(add_pop %>%
#                               filter(NUMP > 0 & CNSY=="2016")%>%
#                                 mutate(YARP_BANDS=ifelse(
#       YARP >= 2012, "0-4 years since immigration", ifelse(
#         YARP >= 2007 & YARP < 2012, "5-9 years since immigration", ifelse(
#           YARP >= 2002 & YARP < 2007, "10-14 years since immigration",ifelse(
#             YARP >= 1997 & YARP < 2002, "15-19 years since immigration",ifelse(
#               YARP >= 1000 & YARP < 1997, "20+ years since immigration", "No value"))))))%>%
#     group_by(YARP_BANDS, AGE_BANDS)%>%
#     summarise(tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
#     tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
#     tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))
#               #tbi_prev_hi = (sum(LTBP.high)/sum(NUMP))*100,
#               #tbi_prev_low = (sum(LTBP.low)/sum(NUMP))*100)
# 
# View(tbi_yarp_agep_tabprep_total)

```


# Age at Immigration and TB Disease Incidence in Country of Origin
```{r aarp_inc, figures-side, fig.show="hold", out.width="50%", echo=FALSE}

#View(add_pop)

#View(add_pop)
tbi_age_inc_tabprep <- unique(add_pop %>%
                                 filter(NUMP > 0 & !is.na(NUMP))%>%
    group_by(CNSY, AARP_BANDS, inc_band_per100k)%>%
    summarise(proportion_pop=round((sum(NUMP)/tot_pop)*100, 1),
    tbi_prev = round(median(Reduce("+",replace_na(LTBP, replace = 0)))/sum(NUMP)*100,0),
    tbi_prev_95_low = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.025)/sum(NUMP)*100,0),
    tbi_prev_95_high = round(quantile(Reduce("+",replace_na(LTBP, replace = 0)), 0.975)/sum(NUMP)*100,0)))
    
View(tbi_age_inc_tabprep)

```


Put into list to export to Excel for re-naming columns and formatting
```{r}
output_list <- list(summary_aarp,
                    summary_agep,
                    overall_prevalence
                    pop_aarp_by_census,
                    pop_coo_by_census,
tbi_prev_coo_by_census,
tbi_age_tabprep,
tbi_inc_tab,
tbi_2years_imm,
tbi_2years_imm_inc_band,
tbi_yarp_agep_med,
tbi_yarp_agep_low,
tbi_yarp_agep_high,
tbi_yarp_inc_tabprep_total,
                    tbi_age_inc_tabprep)

write_xlsx(output_list, "/Users/ajordan/Library/CloudStorage/OneDrive-McGillUniversity/A TB/Project Writing/TBI Prev Pub/tbi_prevalence_tables.xlsx")
```

